---
title: "MMM_tweets"
author: "Marc Kissel"
date: "2/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r needed libraries}
library(rtweet)
library(tidyverse)
library(tidytext)
library(wordcloud)
library(wordcloud2)
library(lubridate)
```


first load the tweets

```{r}
MMM_2020<- search_tweets(
  "#2020MMM", n = 18000, include_rts = FALSE) 

Sys.time()


MMM_2020_March02_6_30_am<- search_tweets(
  "#2020MMM", n = 18000, include_rts = FALSE) 


MMM_2020_March02_3_30_pm<- search_tweets(
  "#2020MMM", n = 18000, include_rts = FALSE) 

MMM_2020_March03_12_15_pm<- search_tweets(
  "#2020MMM", n = 18000, include_rts = FALSE) 


MMM_2020_March04_11_30_am<- search_tweets(
  "#2020MMM", n = 18000, include_rts = FALSE)

MMM_2020_March04_11_30_am<- search_tweets(
  "#2020MMM", n = 18000, include_rts = FALSE)


MMM_2020_March04_8_45_pm<- search_tweets(
  "#2020MMM", n = 18000, include_rts = FALSE)




current_time <- Sys.time()
```

now i loose the first 29 from set1 and

Export data

```{r}

write_as_csv(MMM_2020, "2020-03-01_9AM_tweets")
write_as_csv(MMM_2020_b_March03_5_50_pm, "2020-03-01_5_50pm_tweets")
write_as_csv(MMM_2020_March02_6_30_am, "2020-03-02_6_30am_tweets")
write_as_csv(MMM_2020_March02_3_30_pm, "2020-03-02_3_30pm_tweets")
write_as_csv(MMM_2020_March03_12_15_pm, "2020-03-03_12_15pm_tweets")
write_as_csv(MMM_2020_March04_11_30_am,"2020-03-04_11_30am_tweets" )
write_as_csv(MMM_2020_March04_8_45_pm,"2020-03-04_8_45pm_tweets" )



```

Testing adding dfs together
```{r}
first <- read_csv("2020-03-01_9AM_tweets.csv")
second <- read_csv("2020-03-01_5_50pm_tweets.csv")
third <- read_csv("2020-03-02_6_30am_tweets.csv")
fourth <- read_csv("2020-03-02_3_30pm_tweets.csv")
fifth <- read_csv("2020-03-03_12_15pm_tweets.csv")
sixth <-read_csv("2020-03-04_11_30am_tweets.csv")
seventh <- read_csv("2020-03-04_8_45pm_tweets.csv")

all_tweets <- rbind(first, second, third, fourth, fifth, sixth, seventh) %>% distinct(text, .keep_all = TRUE)

#total <- rbind(a,b)
#totalgrouped <- total %>%  distinct(text, .keep_all = TRUE)
#MMM_2020 <- totalgrouped

```



Basic graphs 

```{r}
ts_plot(all_tweets, "2 hours") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of #2020MMM Twitter statuses",
    subtitle = paste("as of", current_time ),
    caption = "\nSource: Data collected from Twitter's REST API via rtweet")
  
  

ggplot(all_tweets, aes(created_at))+
  geom_density(alpha=.75, fill="#4cda76")+ # fill with main SAC logo blue
  ggtitle("#2020MMM Tweets")+
  ylab("Density of tweets")+
  xlab("Time")

ggplot(all_tweets, aes(created_at))+
  geom_density(alpha=.75, fill="#4cda76") + labs(title = "Frequency of #2020MMM Twitter statuses",
    subtitle = paste("as of", current_time ),
    caption = "\nSource: Data collected from Twitter's REST API via rtweet")
    


```



anaylze data

```{r}
all_tweets %>% count(screen_name, sort=T)
all_tweets %>% group_by(screen_name) %>% summarise(rt = sum(retweet_count)) %>% arrange(-rt)

MMM_2020 %>% arrange(-favorite_count) %>% select(favorite_count)

MMM_2020 %>% group_by(screen_name) %>% count(sort=T)

MMM_2020 %>% group_by(screen_name) %>% filter(n() > 5) %>%  ggplot(aes(x= screen_name)) + geom_bar() + coord_flip()



a <- all_tweets %>% group_by(screen_name) %>% add_tally() %>%   filter(n() > 5) %>% ungroup()

a %>% mutate(screen_name = fct_reorder(screen_name,n)) %>% ggplot(aes(x= screen_name, fill=screen_name)) + geom_bar() + coord_flip() + labs(title = "number of tweets that mention #2020MMM", subtitle = paste("as of", current_time ), x= "screen name") + theme(legend.position = "none")


truth_background <- png::readPNG("LoveMMM.png")

annotation_custom(rasterGrob(truth_background, 
                                 width = unit(1,"npc"), 
                                 height = unit(1,"npc")), 
                      -Inf, Inf, -Inf, Inf) 

library(grid)

a %>% mutate(screen_name = fct_reorder(screen_name,n)) %>% ggplot(aes(x= screen_name, fill=screen_name)) + 
  annotation_custom(rasterGrob(truth_background, 
                                 width = unit(1,"npc"), 
                                 height = unit(1,"npc")), 
                      -Inf, Inf, -Inf, Inf)  +
  geom_bar() + coord_flip() + labs(title = "number of tweets by username that mention #2020MMM", subtitle = paste("as of", current_time ), x= "screen name", caption = "background img from: https://libguides.asu.edu/MarchMammalMadness") + theme(legend.position = "none")  
  
  

all_tweets %>% mutate(day = as_date(created_at)) %>% count(day, sort=T)

```


wordcloud
note: if there is a _ not showing up, which exmapling why mammls_suck isn't there

```{r}
MMM_table <- all_tweets %>% unnest_tokens(word, text)
MMM_table <- MMM_table %>% anti_join(stop_words)
MMM_table <- MMM_table %>% count(word, sort =  T)
MMM_table_edited <- MMM_table %>% filter(!word %in% c("2020mmm", "t.co", "https"))
wordcloud2::wordcloud2(MMM_table_edited, size = .4)
#MMM_table_edited <- MMM_table %>% filter(!word %in% c("2020mmm", "t.co", "https", "march", "mammal", "madness"))


letterCloud(MMM_table_edited, word = "M", size=.4)

filt <- MMM_table_edited %>%  filter(n >10)

figPath <- "/Users/mkissel/Documents/Code/R_projects/2020_MMM/image.png"


wordcloud2(demoFreq, figPath = figPath, size = 3,color = "green", backgroundColor = "black")
```



more text

```{r}
team <- MMM_2020 %>% filter(str_detect(text, "team"))

filter(str_detect(text, "panda")) %>% pull(text)

#lets see if i can pull out teams? or remove screennames from text

teams <- all_tweets %>% filter(str_detect(text, "team"))



MMM_table_edited
```


map data
(note that most tweets don't have loc data)

```{r}
MMM_2020 %>% count(country_code)
rt1 <- lat_lng(all_tweets)
```


map itself, version 1

```{r}
par(mar = c(0, 0, 0, 0))
maps::map("world", lwd = .25)
with(rt1, points(lng, lat, pch = 20, cex = .75, col = rgb(0, .3, .7, .75)))

```

map, version 2 w/ leaflet 

```{r}
library(leaflet)
leaflet() %>% addTiles() %>% 
  setView(lat = 50.85045, lng = 4.34878, zoom=0) %>%  addMarkers(~lng, ~lat, data = rt1, popup = ~as.character(text), label = ~as.character(screen_name)) 
```


stream data:
example from https://rtweet.info/articles/stream.html#stream_tweets


```{r}
q <- "2020MMM"
library(tidygraph)

## Stream time in seconds so for one minute set timeout = 60
## For larger chunks of time, I recommend multiplying 60 by the number
## of desired minutes. This method scales up to hours as well
## (x * 60 = x mins, x * 60 * 60 = x hours)

## Stream for 30 minutes
streamtime <- 30 * 60 ## Stream for 30 minutes
streamtime <- 30 * 1 
filename <- "rtelect.json"
rt <- stream_tweets("2020MMM", timeout = 90, file_name = filename) # do or 9 seconds

library(rjson)
result <- fromJSON(file = "rtelect.json")
```


network?
https://rud.is/books/21-recipes/visualizing-a-graph-of-retweet-relationships.html


```{r}
library(tidygraph)
library(rtweet)
library(igraph)
library(hrbrthemes)
library(ggraph)
library(tidyverse)

filter(MMM_2020, retweet_count > 0) %>% 
  select(screen_name, mentions_screen_name) %>%
  unnest(mentions_screen_name) %>% 
  filter(!is.na(mentions_screen_name)) %>% 
  graph_from_data_frame() -> rt_g



ggplot(data_frame(y=degree_distribution(rt_g), x=1:length(y))) +
  geom_segment(aes(x, y, xend=x, yend=0), color="slateblue") +
  scale_y_continuous(expand=c(0,0), trans="sqrt") +
  labs(x="Degree", y="Density (sqrt scale)", title="#rstats Retweet Degree Distribution") +
  theme_ipsum_rc(grid="Y", axis="x")



#add labels for nodes that have a degree of 20 or more 
V(rt_g)$node_label <- unname(ifelse(degree(rt_g)[V(rt_g)] > 20, names(V(rt_g)), "")) 
V(rt_g)$node_size <- unname(ifelse(degree(rt_g)[V(rt_g)] > 20, degree(rt_g), 0)) 


ggraph(rt_g, layout = 'linear', circular = TRUE) + 
  geom_edge_arc(edge_width=0.125, aes(alpha=..index..)) +
  geom_node_label(aes(label=node_label, size=node_size),
                  label.size=0, fill="#ffffff66", segment.colour="springgreen",
                  color="slateblue", repel=TRUE, family=font_rc, fontface="bold") +
  coord_fixed() +
  scale_size_area(trans="sqrt") +
  labs(title="Retweet Relationships", subtitle="Most retweeted screen names labeled. Darkers edges == more retweets. Node size == larger degree") +
  theme_graph(base_family=font_rc) +
  theme(legend.position="none")




rt_g %>% ggraph(layout = "fr") +
        geom_edge_link() +
        geom_node_point(color = "darkslategray4", size = 5) +
        geom_node_text(aes(label = name), vjust = 1.8) +
        ggtitle(expression(paste("Word Network in Jane Austen's ", 
                                 italic("Pride and Prejudice")))) +
        theme_void()
  


rt_g %>% ggraph(layout = "fr") +
        geom_edge_link() +
        geom_node_point(color = "darkslategray4", size = 5) +
  geom_node_label(aes(label=node_label, size=node_size),
                  label.size=0, fill="#ffffff66", segment.colour="springgreen",
                  color="slateblue", repel=TRUE, family=font_rc, fontface="bold")      +
        ggtitle(expression(paste("Who talks to who in", 
                                 italic("March Mammal Madness")))) +
        theme_void()
  

  


#other visal
#http://pablobarbera.com/big-data-upf/html/02a-networks-intro-visualization.html


plot(rt_g)


plot(rt_g,
     vertex.color = "grey", # change color of nodes
     vertex.label.color = "black", # change color of labels
     vertex.label.cex = .75, # change size of labels to 75% of original size
     edge.curved=.25, # add a 25% curve to the edges
     edge.color="grey20") # change edge color to grey

V(rt_g)$size <- strength(rt_g)
par(mar=c(0,0,0,0)); plot(rt_g)


#log


V(rt_g)$size <- log(strength(rt_g)) * 4 + 3
par(mar=c(0,0,0,0)); plot(rt_g)


#deal with names?


V(rt_g)$label <- ifelse( strength(rt_g)>=5, V(rt_g)$name, NA )
par(mar=c(0,0,0,0)); plot(rt_g)


#circle

V(rt_g)$label <- ifelse( strength(rt_g)>=2, V(rt_g)$name, NA )
par(mar=c(0,0,0,0))
plot(rt_g,  layout=layout_in_circle, main="Circle")


V(rt_g)$label <- ifelse( degree(rt_g)>=20, V(rt_g)$name, NA )
par(mar=c(0,0,0,0))
plot(rt_g,  layout=layout_in_circle, main="Circle")


#The most popular layouts are force-directed. These algorithms, such as Fruchterman-Reingold, try to position the nodes so that the edges have similar length and there are as few crossing edges as possible. The idea is to generate “clean” layouts, where nodes that are closer to each other share more connections in common that those that are located further apart. Note that this is a non-deterministic algorithm: choosing a different seed will generate different layouts.


#force-directed


par(mfrow=c(1,2))
set.seed(777)
fr <- layout_with_fr(rt_g, niter=1000)
par(mar=c(0,0,0,0)); plot(rt_g, layout=fr)
set.seed(666)
fr <- layout_with_fr(rt_g, niter=1000)
par(mar=c(0,0,0,0)); plot(rt_g, layout=fr)



#more
#https://juliasilge.com/blog/life-changing-magic/





rt_g %>% 
   ggraph(layout = "fr") +
        geom_edge_link(aes(edge_alpha = n, edge_width = n)) +
        geom_node_point(color = "darkslategray4", size = 5) +
        geom_node_text(aes(label = name), vjust = 1.8) +
        ggtitle(expression(paste("Word Network in Jane Austen's ", 
                                 italic("Pride and Prejudice")))) +
        theme_void()


#blah for above


filter(all_tweets, retweet_count > 0) %>% 
  select(screen_name, mentions_screen_name) %>%
  unnest(mentions_screen_name) %>%
    filter(!is.na(mentions_screen_name)) %>%  
  pivot_longer(cols = mentions_screen_name, names_to = "mentions")
  
```



ABOVE IS kinda messy
http://graphtweets.john-coene.com/



BELOw looks nicer

```{r}
install.packages("graphTweets")
install.packages("sigmajs")
library(graphTweets)
library(sigmajs)

#lest stats by adding te dfs togehte tthat eep the ino in list forms

x <- rbind(MMM_2020_b_March03_5_50_pm, MMM_2020_March02_6_30_am, MMM_2020_March02_3_30_pm, MMM_2020_March03_12_15_pm, MMM_2020_March04_11_30_am)

 x %>% distinct(text, .keep_all = TRUE)
  
  
x %>% gt_edges(text, screen_name, status_id) %>% 
  gt_graph() %>% 
  plot() #bad

######

MMM_2020 %>% 
  gt_edges(screen_name, mentions_screen_name) %>% 
  gt_nodes(meta = TRUE) %>% 
  gt_collect() -> graph

#smaller
MMM_2020_small <- MMM_2020 %>% filter(!is.na(mentions_screen_name)) %>% gt_edges(screen_name, mentions_screen_name) %>% 
  gt_nodes(meta = TRUE) %>% 
  gt_collect() -> graph


MMM_2020 %>% 
  gt_edges(screen_name, mentions_screen_name) %>% 
  gt_nodes() %>% 
  gt_collect() -> gt

nodes <- gt$nodes %>% 
  mutate(
    id = nodes,
    label = nodes,
    size = n,
    color = "#1967be"
  ) 

edges <- gt$edges %>% 
  mutate(
    id = 1:n()
  )

sigmajs() %>% 
  sg_force_start() %>% 
  sg_nodes(nodes, id, label, size, color) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_force_stop(10000)


sigmajs() %>% 
  sg_force_start() %>% 
  sg_nodes(nodes, id, label, size, color) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_force_stop(10000) %>%  sg_drag_nodes() %>% sg_cluster()


#########################################3
#try various things fomr http://sigmajs.john-coene.com/articles/cluster.html etc
#

MMM_2020 %>% filter(!is.na(mentions_screen_name)) %>% 
  gt_edges(screen_name, mentions_screen_name) %>% 
  gt_nodes() %>% 
  gt_collect() -> gt





####################3

net <- all_tweets %>% 
  gt_edges(screen_name, hashtags) %>% 
  gt_nodes() %>% 
  gt_collect()

edges <- net$edges
nodes <- net$nodes

edges$id <- seq(1, nrow(edges))
nodes$id <- nodes$nodes
nodes$label <- nodes$nodes
nodes$size <- nodes$n
nodes$color <- ifelse(nodes$type == "user", "#0084b4", "#1dcaff")


sigmajs() %>% 
  sg_force_start() %>% 
  sg_nodes(nodes, id, label, size, color) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_force_stop(10000)

#to deal with multple maybe this will work

net <- MMM_2020_b_March03_5_50_pm %>% 
  gt_co_edges(mentions_screen_name) %>%
  gt_nodes() %>% 
  gt_collect()

c(edges, nodes) %<-% net

edges <- edges %>% 
  mutate(id = 1:n()) 

nodes <- nodes %>% 
  mutate(
    id = nodes,
    label = id,
    size = n
  )

sigmajs() %>% 
  sg_nodes(nodes, id, label, size) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_cluster(
    colors = c(
      "#0084b4",
      "#00aced",
      "#1dcaff",
      "#c0deed"
      )
  ) %>% 
  sg_layout(layout = igraph::layout.fruchterman.reingold) %>% 
  sg_neighbours() %>% 
  sg_settings(
    maxNodeSize = 3,
    defaultEdgeColor = "#a3a3a3",
    edgeColor = "default"
  )

#ok, above works but aisl on all_tweets. i think tis is becuase, all_tweets has the mentons_scren ame as charte not as a list...can weix or is it fucked
#also check if that iw whyother lok weird


#update it is! so can i read them back in as a list?
#OR keep what i have and bind togehter to avoit raeding in
#or fix all_tweet
#or we can just do it by day? i wonder how many twett for each battle day?

w <- all_tweets %>% as.list(mentions_screen_name)

```


#below shld work!!!!!
```{r}
tidy_tweets <- all_tweets %>% 
  select(screen_name, mentions_screen_name) %>% 
  mutate(
    hashtags = gsub("\\[|\\]|'", "", mentions_screen_name)
  ) %>% 
  tidyr::separate_rows(hashtags, sep = ", ") %>% 
  tidyr::nest(hashtags = c(hashtags))




tidy_tweets <- all_tweets %>% 
  select(screen_name, mentions_screen_name) %>% 
  tidyr::separate_rows(mentions_screen_name, sep = " ") %>% 
  tidyr::nest(mentions_screen_name = c(mentions_screen_name))

tidy_tweets$mentions_screen_name <- tidy_tweets$mentions_screen_name %>%  
  purrr::map(unlist) %>% 
  purrr::map(unname)


tidy_tweets %>% 
  gt_edges(screen_name, mentions_screen_name) %>% 
  gt_nodes() %>% 
  gt_collect() -> gt

nodes <- gt$nodes %>% 
  mutate(
    id = nodes,
    label = nodes,
    size = n,
    color = "#1967be"
  ) 

edges <- gt$edges %>% 
  mutate(
    id = 1:n()
  )

sigmajs() %>% 
  sg_force_start() %>% 
  sg_nodes(nodes, id, label, size, color) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_force_stop(10000) %>%  sg_drag_nodes() %>% sg_cluster()


sigmajs() %>% 
  sg_force_start() %>% 
  sg_nodes(nodes, id, label, size, color) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_force_stop(10000)


#what about comentions?

net <- tidy_tweets %>% 
  gt_co_edges(mentions_screen_name) %>%
  gt_nodes() %>% 
  gt_collect()

c(edges, nodes) %<-% net


edges <- edges %>% 
  mutate(id = 1:n()) 

nodes <- nodes %>% 
  mutate(
    id = nodes,
    label = id,
    size = n
  )

sigmajs() %>% 
  sg_nodes(nodes, id, label, size) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_cluster(
    colors = c(
      "#0084b4",
      "#00aced",
      "#1dcaff",
      "#c0deed"
      )
  ) %>% 
  sg_layout(layout = igraph::layout.fruchterman.reingold) %>% 
  sg_neighbours() %>% 
  sg_settings(
    maxNodeSize = 3,
    defaultEdgeColor = "#a3a3a3",
    edgeColor = "default"
  )



g %>% 
  gt_edges(screen_name, mentions_screen_name) %>% 
  gt_nodes(meta = TRUE) %>% 
  gt_collect() -> graph


```




belwo is more on the graphTweets etc

rom:https://twinetbook.john-coene.com/get-started.html

```{r}
net <- tidy_tweets %>% 
  gt_edges(source = screen_name, target = mentions_screen_name)

class(net)

#To extracts the results from graphTweets run gt_collect, this will work at any point in the chain of pipes (%>%).

net <- net %>% 
  gt_collect()
#Great but this returns a lists and R users much prefer data.frames. graphTweets actualy returns two data.frames that are encapsulated in a list. Indeed networks cannot be compressed into a single data.frame, we need 1) nodes and 2) edges.

names(net)

#reat, so it looks like we have both nodes and edges, not really. We only have edges, net$nodes is actually NULL.

# hindsights, we only ran gt_edges so it make sense to only have edges. Let’s scrap that and get both nodes and edges.


net <- all_tweets %>% 
  gt_edges(screen_name, mentions_screen_name) %>% # get edges
  gt_nodes() %>% # get nodes
  gt_collect() # collect

lapply(net, class)

#unpack netowrk


c(edges, nodes) %<-% net

head(edges)


#each edge simply consists of a source and a target. In this network, the source essentially corresponds to screen_name passed in gt_edges, it is the user who posted the tweet. In contrast, target includes the users that were tagged in the text of the tweet. The n variable indicates how many tweets connect the source to the target.

head(nodes)

n the nodes data frame, the column n is the number of times the node appears (whether as source or as target), while the nodes column are the Twitter handles of both the authors of the tweets (screen_name) and those who were @tagged in the tweets. All nodes are of type user in this network, but we will have examples later in the book where it may not be.



#Below we rename a few columns, to meet sigmajs’ naming convention.
#We add ids to our nodes, this can be a string and thus simply corresponds to our nodes column.
#We essentially rename n to size as this is what sigmajs understands.
#We add ids to our edges as sigmajs requires each edge to have a unique id.


nodes$id <- as.factor(nodes$nodes) 
nodes$size <- nodes$n 
edges$id <- seq(1, nrow(edges))

#sigmajs has a specific but sensible naming convention as well as basic minimal requirements.
#Nodes must at least include id, and size.
#Edges must at least include id, source, and target.

#Actually, the twinetverse comes with helper functions to prepare the nodes and edges built by graphTweets for use in sigmajs (these are the only functions the ’verse provides).

nodes <- nodes2sg(nodes)
edges <- edges2sg(edges)

#Let’s visualise that, we must initialise every sigmajs graph with the sigmajs function, then we add our nodes with sg_nodes, passing the column names we mentioned previously, id, and size to meet sigmajs’ minimum requirements. In sigmajs, at the exception of the function called sigmajs, all start with sg_

sigmajs() %>% 
  sg_nodes(nodes, id, size) 

#igmajs actually allows you to build graphs using only nodes or edges, we’ll see why this is useful in a later chapter on temporal graphs. Let’s add the edges. Then again, to meet sigmajs’ requirements, we pass id, source and target.

sigmajs() %>% 
  sg_nodes(nodes, id, size) %>% 
  sg_edges(edges, id, source, target)

#Nevermind beauty, what’s on the graph exactly? Each disk/point on the graph is a twitter user, they are connected when one has tagged the other in the a tweet.

#You may also notice that the graph contains surprisingly few nodes, given that we queried 100 tweets you would expect over 100 nodes on the graph. This is because our visualisation only includes tweets that mention other users and most tweets are not targeted (tagged) at other users. There is an easy remedy to this which we’ll look at in the next section.

#compare to

sigmajs("webgl") %>% 
  sg_nodes(nodes, id, size) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_layout(layout = igraph::layout_components) %>% 
  sg_cluster(
    colors = c(
      "#0075a0",
      "#0084b4",
      "#00aced",
      "#1dcaff",
      "#c0deed"
      )
  ) %>% 
  sg_settings(
    minNodeSize = 1,
    maxNodeSize = 2.5,
    edgeColor = "default",
    defaultEdgeColor = "#d3d3d3"
  )

```



to think about.
1. could look at , linking users to the users they retweet to fundamentally visualise how information spreads throughout Twitter.